Highcharter Handbook

### 2019-08-09 04_highcharter-handbook/highcharter-handbook.Rmd
HC handbook update

library(highcharter)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

@@

## Basics

@@

### Numeric Vector -> Histogram

```{r}
starwars %>%
  pull(mass) %>%
  hchart()
```

### R Density Object -> Density Plot

```{r}
starwars %>%
  filter(!is.na(mass)) %>%
  pull(mass) %>%
  density() %>%
  hchart()
```

### Forecast Object -> Timeseries / Forecast Chart

## Links

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

library(highcharter)
library(tidyverse)
library(forecast)
knitr::opts_chunk$set(echo = TRUE)
```

@@

## Datasets

I'll frequently be using the following two datasets:

* dplyr::starwars | the physical traits and info for characters in the starwars films
* dplyr::storms | hurricane timeseries data

Various other object types are supported which you can find [here](http://jkunst.com/highcharter/hchart.html)

### Numeric Vector :: Histogram

```{r}
starwars %>%
  pull(mass) %>%
  hchart(name = class(.))
```

### Density Object :: Density Plot

```{r}
starwars %>%
  filter(!is.na(mass)) %>%
  pull(mass) %>%
  density() %>%
  hchart(name = class(.))
```

### Forecast Object :: Timeseries / Forecast Chart

```{r}
storms %>%
  filter(name == "Emily") %>%
  pull(wind) %>%
  forecast() %>%
  hchart(name = class(.))
```

## hchart() + hcaes()

The most practical use of `hchart()` however is to use it like you would the `ggplot()` function. The implementation is slightly different - you have to specify your geom type inside the `hchart()` call for example - but the

@@
